---
title: 'Master Temp Logger Code'
author: "ZachHorstman"
date: "1/14/2021"
output:
  pdf_document: default
  html_document: default
---

# This report includes every known temperature logger we have recovered (2015-2020). Sites are listed in alphabetical order. Use the Index on the left to easily navigate to graphs.

## Note: Some recorded temperatures may have been of air temperature if stream dried up. 
```{r, echo=FALSE}
library(RODBC)
library(tidyverse)

con <- odbcDriverConnect("Driver={Microsoft Access Driver (*.mdb, *.accdb)};DBQ=W:/Fisheries/Rivers and Streams Program/Temp Loggers/TemperatureLoggers.accdb")

#if adding a new site, simply copy and paste a line here and add the new line of code here.
# This chunk will take a minute to run all the lines of code...That's a lot of data.

sqlFetch(con, 'AID') -> AID
sqlFetch(con, 'Bone_Site1') -> Bone_Site1
sqlFetch(con, 'Bone_Site2') -> Bone_Site2
sqlFetch(con, 'Bone_Site3') -> Bone_Site3
sqlFetch(con, 'Bone_Site4') -> Bone_Site4
sqlFetch(con, 'Bordeaux_Cliffs') -> Bordeaux_Cliffs
sqlFetch(con, 'Bordeaux_North') -> Bordeaux_North
sqlFetch(con, 'Cedar_Site1') -> Cedar_Site1
sqlFetch(con, 'Chadron_AboveDischarge') -> Chadron_AboveDischarge
sqlFetch(con, 'Chadron_BelowDischarge') -> Chadron_BelowDischarge
sqlFetch(con, 'Chadron_CCRHeadwaters') -> Chadron_CCRHeadwaters
sqlFetch(con, 'Chadron_ParkEntrance') -> Chadron_ParkEntrance
sqlFetch(con, 'Chadron_ParkExit') -> Chadron_ParkExit
sqlFetch(con, 'Deadmans') -> Deadmans
sqlFetch(con, 'Dismal_Dunning') -> Dismal_Dunning
sqlFetch(con, 'Dry_Site1') -> Dry_Site1
sqlFetch(con, 'DrySpottedtail_Hanson') -> DrySpottedtail_Hanson
sqlFetch(con, 'DrySpottedtail_Steffl') -> DrySpottedtail_Steffl
sqlFetch(con, 'EastAsh_USFS') -> EastAsh_USFS
sqlFetch(con, 'Evergreen_Site1') -> Evergreen_Site1
sqlFetch(con, 'Gordon_Site1') -> Gordon_Site1
sqlFetch(con, 'Gordon_Site2') -> Gordon_Site2
sqlFetch(con, 'Gordon_Site3') -> Gordon_Site3
sqlFetch(con, 'Gordon_Site4') -> Gordon_Site4
sqlFetch(con, 'Holt_WMA') -> Holt_WMA
sqlFetch(con, 'Larabee_Dolezal') -> Larabee_Dolezal
sqlFetch(con, 'Larabee_Forney') -> Larabee_Forney
sqlFetch(con, 'Larabee_School') -> Larabee_School
sqlFetch(con, 'LongPine_Site2') -> LongPine_Site2
sqlFetch(con, 'LongPine_Site3') -> LongPine_Site3
sqlFetch(con, 'LongPine_Site4') -> LongPine_Site4
sqlFetch(con, 'LongPine_Site6') -> LongPine_Site6
sqlFetch(con, 'MiddleLoup_MiddleBranch') -> MiddleLoup_MiddleBranch
sqlFetch(con, 'MiddleLoup_Mullens') -> MiddleLoup_Mullens
sqlFetch(con, 'MiddleLoup_SouthBranch') -> MiddleLoup_SouthBranch
sqlFetch(con, 'Minnechaduza_Site1') -> Minnechaduza_Site1
sqlFetch(con, 'Minnechaduza_Site2') -> Minnechaduza_Site2
sqlFetch(con, 'Minnechaduza_Site3') -> Minnechaduza_Site3
sqlFetch(con, 'Monroe') -> Monroe
sqlFetch(con, '9Mile_Lower') -> NineMileLower
sqlFetch(con, '9Mile_OFW') -> NineMileOFW
sqlFetch(con, '9Mile_WMA') -> NineMileWMA
sqlFetch(con, 'Niobrara_HWY71') -> Niobrara_HWY71
sqlFetch(con, 'Niobrara_HWY385') -> Niobrara_HWY385
sqlFetch(con, 'Niobrara_Schoolhouse') -> Niobrara_Schoolhouse
sqlFetch(con, 'Pine_Middle') -> Pine_Middle
sqlFetch(con, 'Pine_North') -> Pine_North
sqlFetch(con, 'Pine_South') -> Pine_South
sqlFetch(con, 'Plum_Site1') -> Plum_Site1
sqlFetch(con, 'Plum_Site2') -> Plum_Site2
sqlFetch(con, 'Plum_Site3') -> Plum_Site3
sqlFetch(con, 'Plum_Site4') -> Plum_Site4
sqlFetch(con, 'Plum_Site5') -> Plum_Site5
sqlFetch(con, 'Plum_Site6') -> Plum_Site6
sqlFetch(con, 'Plum_Site7') -> Plum_Site7
sqlFetch(con, 'Plum_Site8') -> Plum_Site8
sqlFetch(con, 'Plum_Site9') -> Plum_Site9
sqlFetch(con, 'SandDraw_Site1') -> SandDraw_Site1
sqlFetch(con, 'SandDraw_Site2') -> SandDraw_Site2
sqlFetch(con, 'Schlagel_newWMA') -> Schlagel_newWMA
sqlFetch(con, 'Schlagel_Swanson') -> Schlagel_Swanson
sqlFetch(con, 'Schlagel_Vanderplow') -> Schlagel_Vanderplow
sqlFetch(con, 'Schlagel_WMA') -> Schlagel_WMA
sqlFetch(con, 'Sheep_Site1') -> Sheep_Site1
sqlFetch(con, 'Sheep_Site2') -> Sheep_Site2
sqlFetch(con, 'Snake_Adamson') -> Snake_Adamson
sqlFetch(con, 'Snake_HWY61') -> Snake_HWY61
sqlFetch(con, 'Snake_Upper') -> Snake_Upper
sqlFetch(con, 'Soldier_MiddleBranch') -> Soldier_MiddleBranch
sqlFetch(con, 'Sowbelly') -> Sowbelly
sqlFetch(con, 'WestAsh_USFS') -> WestAsh_USFS
sqlFetch(con, 'White_Andrews') -> White_Andrews
sqlFetch(con, 'White_EastFtRob') -> White_EastFtRob
sqlFetch(con, 'White_GolfCourse') -> White_GolfCourse
sqlFetch(con, 'White_SwingingBridge') -> White_SwingingBridge
sqlFetch(con, 'WhiteClay') -> WhiteClay 
sqlFetch(con, 'Willow_Site1') -> Willow_Site1

sqlFetch(con, 'LoggerLocations') -> LoggerLocations # current logger locations
colnames(LoggerLocations)[colnames(LoggerLocations)=="Logger Name"] <- "LoggerName"

odbcClose(con)
```


```{r, echo=FALSE, include=FALSE}
# Interactive Map of each logger location.
library(tmap)
library(sf)

#set the map to interactive viewing --so you can click on the points
tmap_mode("view")

#Put data in a format for sf 
mapdata <- st_as_sf(LoggerLocations, coords = c("Longitude", "Latitude"), crs = 4326)

tmap_options(max.categories = 34)

#make a pretty map
allmapdata <- tm_shape(mapdata)+
  #Add basemap
  tm_basemap(server = c('https://basemap.nationalmap.gov/arcgis/rest/services/USGSImageryTopo/MapServer/tile/{z}/{y}/{x}')) +
  #add points to map with color changing by ID. 
  #"popup.vars" determines what is shown when a location is selected
  tm_symbols(col = "Waterbody", 
             palette = "Dark2", alpha = 0.75,
             #title.size = "Logger_Name",
             #title.col = "Logger_Name", id = "Logger_Name",
             popup.vars = c("Waterbody", "Site"),
             #size = 10,
             style = "pretty",
             clustering = F) +
  tm_layout(legend.outside = T) +
  tm_view(symbol.size.fixed = T)

allmapdata
```

# Alliance Drainage
```{r, echo=FALSE, warning=FALSE}
#get data
AIDdata<- AID%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  AIDdata$tempRange = "Cool"
  AIDdata$tempRange[AIDdata$Temp < 68] <- "Cold"
  AIDdata$tempRange[AIDdata$Temp >= 77] <- "Warm"
  AIDdata$tempRange <- factor(AIDdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = AIDdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Alliance Drainage") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Bone Creek - Site 1
```{r, echo=FALSE, warning=FALSE}
#get data
Bone_Site1data<- Bone_Site1%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Bone_Site1data$tempRange = "Cool"
  Bone_Site1data$tempRange[Bone_Site1data$Temp < 68] <- "Cold"
  Bone_Site1data$tempRange[Bone_Site1data$Temp >= 77] <- "Warm"
  Bone_Site1data$tempRange <- factor(Bone_Site1data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Bone_Site1data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Bone Creek - Site 1") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Bone Creek - Site 2
```{r, echo=FALSE, warning=FALSE}
#get data
Bone_Site2data<- Bone_Site2%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Bone_Site2data$tempRange = "Cool"
  Bone_Site2data$tempRange[Bone_Site2data$Temp < 68] <- "Cold"
  Bone_Site2data$tempRange[Bone_Site2data$Temp >= 77] <- "Warm"
  Bone_Site2data$tempRange <- factor(Bone_Site2data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Bone_Site2data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Bone Creek - Site 2") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Bone Creek - Site 3
```{r, echo=FALSE, warning=FALSE}
#get data
Bone_Site3data<- Bone_Site3%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Bone_Site3data$tempRange = "Cool"
  Bone_Site3data$tempRange[Bone_Site3data$Temp < 68] <- "Cold"
  Bone_Site3data$tempRange[Bone_Site3data$Temp >= 77] <- "Warm"
  Bone_Site3data$tempRange <- factor(Bone_Site3data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Bone_Site3data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Bone Creek - Site 3") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Bone Creek - Site 4
```{r, echo=FALSE, warning=FALSE}
#get data
Bone_Site4data<- Bone_Site1%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Bone_Site4data$tempRange = "Cool"
  Bone_Site4data$tempRange[Bone_Site4data$Temp < 68] <- "Cold"
  Bone_Site4data$tempRange[Bone_Site4data$Temp >= 77] <- "Warm"
  Bone_Site4data$tempRange <- factor(Bone_Site4data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Bone_Site4data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Bone Creek - Site 4") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Bordeaux Creek - Cliffs
```{r, echo=FALSE, warning=FALSE}
#get data
Bordeaux_Cliffsdata<- Bordeaux_Cliffs%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Bordeaux_Cliffsdata$tempRange = "Cool"
  Bordeaux_Cliffsdata$tempRange[Bordeaux_Cliffsdata$Temp < 68] <- "Cold"
  Bordeaux_Cliffsdata$tempRange[Bordeaux_Cliffsdata$Temp >= 77] <- "Warm"
  Bordeaux_Cliffsdata$tempRange <- factor(Bordeaux_Cliffsdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Bordeaux_Cliffsdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Bordeaux Creek - Cliffs") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Bordeaux - North
```{r, echo=FALSE, warning=FALSE}
#get data
Bordeaux_Northdata<- Bordeaux_North%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Bordeaux_Northdata$tempRange = "Cool"
  Bordeaux_Northdata$tempRange[Bordeaux_Northdata$Temp < 68] <- "Cold"
  Bordeaux_Northdata$tempRange[Bordeaux_Northdata$Temp >= 77] <- "Warm"
  Bordeaux_Northdata$tempRange <- factor(Bordeaux_Northdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Bordeaux_Northdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Bordeaux Creek - North") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Cedar Creek - Site 1
```{r, echo=FALSE, warning=FALSE}
#get data
Cedar_Site1data<- Cedar_Site1%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Cedar_Site1data$tempRange = "Cool"
  Cedar_Site1data$tempRange[Cedar_Site1data$Temp < 68] <- "Cold"
  Cedar_Site1data$tempRange[Cedar_Site1data$Temp >= 77] <- "Warm"
  Cedar_Site1data$tempRange <- factor(Cedar_Site1data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Cedar_Site1data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Cedar Creek - Site 1") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Chadron Creek - Above Discharge
```{r, echo=FALSE, warning=FALSE}
#get data
Chadron_AboveDischargedata<- Chadron_AboveDischarge%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Chadron_AboveDischargedata$tempRange = "Cool"
  Chadron_AboveDischargedata$tempRange[Chadron_AboveDischargedata$Temp < 68] <- "Cold"
  Chadron_AboveDischargedata$tempRange[Chadron_AboveDischargedata$Temp >= 77] <- "Warm"
  Chadron_AboveDischargedata$tempRange <- factor(Chadron_AboveDischargedata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Chadron_AboveDischargedata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Chadron Creek - Above Discharge") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Chadron Creek - Below Discharge
```{r, echo=FALSE, warning=FALSE}
#get data
Chadron_BelowDischargedata<- Chadron_AboveDischarge%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Chadron_AboveDischargedata$tempRange = "Cool"
  Chadron_AboveDischargedata$tempRange[Chadron_AboveDischargedata$Temp < 68] <- "Cold"
  Chadron_AboveDischargedata$tempRange[Chadron_AboveDischargedata$Temp >= 77] <- "Warm"
  Chadron_AboveDischargedata$tempRange <- factor(Chadron_AboveDischargedata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Chadron_AboveDischargedata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Chadron Creek - Below Discharge") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Chadron Creek - CCR Headwaters (WMA)
```{r, echo=FALSE, warning=FALSE}
#get data
Chadron_CCRHeadwatersdata<- Chadron_CCRHeadwaters%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Chadron_CCRHeadwatersdata$tempRange = "Cool"
  Chadron_CCRHeadwatersdata$tempRange[Chadron_CCRHeadwatersdata$Temp < 68] <- "Cold"
  Chadron_CCRHeadwatersdata$tempRange[Chadron_CCRHeadwatersdata$Temp >= 77] <- "Warm"
  Chadron_CCRHeadwatersdata$tempRange <- factor(Chadron_CCRHeadwatersdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Chadron_CCRHeadwatersdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Chadron Creek - CCR Headwaters (WMA)") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Chadron Creek - Park Entrance
```{r, echo=FALSE, warning=FALSE}
#get data
Chadron_ParkEntrancedata<- Chadron_ParkEntrance%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Chadron_ParkEntrancedata$tempRange = "Cool"
  Chadron_ParkEntrancedata$tempRange[Chadron_ParkEntrancedata$Temp < 68] <- "Cold"
  Chadron_ParkEntrancedata$tempRange[Chadron_ParkEntrancedata$Temp >= 77] <- "Warm"
  Chadron_ParkEntrancedata$tempRange <- factor(Chadron_ParkEntrancedata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Chadron_ParkEntrancedata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Chadron Creek - Park Entrance") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Chadron Creek - Park Exit
```{r, echo=FALSE, warning=FALSE}
#get data
Chadron_ParkExitdata<- Chadron_ParkExit%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Chadron_ParkExitdata$tempRange = "Cool"
  Chadron_ParkExitdata$tempRange[Chadron_ParkExitdata$Temp < 68] <- "Cold"
  Chadron_ParkExitdata$tempRange[Chadron_ParkExitdata$Temp >= 77] <- "Warm"
  Chadron_ParkExitdata$tempRange <- factor(Chadron_ParkExitdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Chadron_ParkExitdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Chadron Creek - Park Exit") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Deadmans Creek
```{r, echo=FALSE, warning=FALSE}
#get data
Deadmansdata<- Deadmans%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Deadmansdata$tempRange = "Cool"
  Deadmansdata$tempRange[Deadmansdata$Temp < 68] <- "Cold"
  Deadmansdata$tempRange[Deadmansdata$Temp >= 77] <- "Warm"
  Deadmansdata$tempRange <- factor(Deadmansdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Deadmansdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Deadmans Creek") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Dismal River - Dunning
```{r, echo=FALSE, warning=FALSE}
#get data
Dismal_Dunningdata<- Dismal_Dunning%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Dismal_Dunningdata$tempRange = "Cool"
  Dismal_Dunningdata$tempRange[Dismal_Dunningdata$Temp < 68] <- "Cold"
  Dismal_Dunningdata$tempRange[Dismal_Dunningdata$Temp >= 77] <- "Warm"
  Dismal_Dunningdata$tempRange <- factor(Dismal_Dunningdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Dismal_Dunningdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Dismal River - Dunning") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Dry Creek - Site 1
```{r, echo=FALSE, warning=FALSE}
#get data
Dry_Site1data<- Dry_Site1%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Dry_Site1data$tempRange = "Cool"
  Dry_Site1data$tempRange[Dry_Site1data$Temp < 68] <- "Cold"
  Dry_Site1data$tempRange[Dry_Site1data$Temp >= 77] <- "Warm"
  Dry_Site1data$tempRange <- factor(Dry_Site1data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Dry_Site1data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Dry Creek - Site 1") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Dry Spottedtail Creek - Hanson
```{r, echo=FALSE, warning=FALSE}
#get data
DrySpottedtail_Hansondata<- DrySpottedtail_Hanson%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  DrySpottedtail_Hansondata$tempRange = "Cool"
  DrySpottedtail_Hansondata$tempRange[DrySpottedtail_Hansondata$Temp < 68] <- "Cold"
  DrySpottedtail_Hansondata$tempRange[DrySpottedtail_Hansondata$Temp >= 77] <- "Warm"
  DrySpottedtail_Hansondata$tempRange <- factor(DrySpottedtail_Hansondata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = DrySpottedtail_Hansondata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Dry Spottedtail Creek - Hanson") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Dry Spottedtail Creek - Steffl
```{r, echo=FALSE, warning=FALSE}
#get data
DrySpottedtail_Steffldata<- DrySpottedtail_Steffl%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  DrySpottedtail_Steffldata$tempRange = "Cool"
  DrySpottedtail_Steffldata$tempRange[DrySpottedtail_Steffldata$Temp < 68] <- "Cold"
  DrySpottedtail_Steffldata$tempRange[DrySpottedtail_Steffldata$Temp >= 77] <- "Warm"
  DrySpottedtail_Steffldata$tempRange <- factor(DrySpottedtail_Steffldata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = DrySpottedtail_Steffldata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Dry Spottedtail Creek - Steffl") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# East Ash Creek - USFS
```{r, echo=FALSE, warning=FALSE}
#get data
EastAsh_USFSdata<- EastAsh_USFS%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  EastAsh_USFSdata$tempRange = "Cool"
  EastAsh_USFSdata$tempRange[EastAsh_USFSdata$Temp < 68] <- "Cold"
  EastAsh_USFSdata$tempRange[EastAsh_USFSdata$Temp >= 77] <- "Warm"
  EastAsh_USFSdata$tempRange <- factor(EastAsh_USFSdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = EastAsh_USFSdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="East Ash Creek - USFS") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Evergreen Creek - Site 1
```{r, echo=FALSE, warning=FALSE}
#get data
Evergreen_Site1data<- Evergreen_Site1%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Evergreen_Site1data$tempRange = "Cool"
  Evergreen_Site1data$tempRange[Evergreen_Site1data$Temp < 68] <- "Cold"
  Evergreen_Site1data$tempRange[Evergreen_Site1data$Temp >= 77] <- "Warm"
  Evergreen_Site1data$tempRange <- factor(Evergreen_Site1data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Evergreen_Site1data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Evergreen Creek - Site 1") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Gordon Creek - Site 1
```{r, echo=FALSE, warning=FALSE}
#get data
Gordon_Site1data<- Gordon_Site1%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Gordon_Site1data$tempRange = "Cool"
  Gordon_Site1data$tempRange[Gordon_Site1data$Temp < 68] <- "Cold"
  Gordon_Site1data$tempRange[Gordon_Site1data$Temp >= 77] <- "Warm"
  Gordon_Site1data$tempRange <- factor(Gordon_Site1data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Gordon_Site1data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Gordon Creek - Site 1") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Gordon Creek - Site 2
```{r, echo=FALSE, warning=FALSE}
#get data
Gordon_Site2data<- Gordon_Site2%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Gordon_Site2data$tempRange = "Cool"
  Gordon_Site2data$tempRange[Gordon_Site2data$Temp < 68] <- "Cold"
  Gordon_Site2data$tempRange[Gordon_Site2data$Temp >= 77] <- "Warm"
  Gordon_Site2data$tempRange <- factor(Gordon_Site2data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Gordon_Site2data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Gordon Creek - Site 2") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Gordon Creek - Site 3
```{r, echo=FALSE, warning=FALSE}
#get data
Gordon_Site3data<- Gordon_Site3%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Gordon_Site3data$tempRange = "Cool"
  Gordon_Site3data$tempRange[Gordon_Site3data$Temp < 68] <- "Cold"
  Gordon_Site3data$tempRange[Gordon_Site3data$Temp >= 77] <- "Warm"
  Gordon_Site3data$tempRange <- factor(Gordon_Site3data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Gordon_Site3data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Gordon Creek - Site 3") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Gordon Creek - Site 4
```{r, echo=FALSE, warning=FALSE}
#get data
Gordon_Site4data<- Gordon_Site4%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Gordon_Site3data$tempRange = "Cool"
  Gordon_Site3data$tempRange[Gordon_Site3data$Temp < 68] <- "Cold"
  Gordon_Site3data$tempRange[Gordon_Site3data$Temp >= 77] <- "Warm"
  Gordon_Site3data$tempRange <- factor(Gordon_Site3data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Gordon_Site3data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Gordon Creek - Site 4") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Holt Creek - WMA
```{r, echo=FALSE, warning=FALSE}
#get data
Holt_WMAdata<- Holt_WMA%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Holt_WMAdata$tempRange = "Cool"
  Holt_WMAdata$tempRange[Holt_WMAdata$Temp < 68] <- "Cold"
  Holt_WMAdata$tempRange[Holt_WMAdata$Temp >= 77] <- "Warm"
  Holt_WMAdata$tempRange <- factor(Holt_WMAdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Holt_WMAdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Holt Creek- WMA") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Larabee Creek - Dolezal
```{r, echo=FALSE, warning=FALSE}
#get data
Larabee_Dolezaldata<- Larabee_Dolezal%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Larabee_Dolezaldata$tempRange = "Cool"
  Larabee_Dolezaldata$tempRange[Larabee_Dolezaldata$Temp < 68] <- "Cold"
  Larabee_Dolezaldata$tempRange[Larabee_Dolezaldata$Temp >= 77] <- "Warm"
  Larabee_Dolezaldata$tempRange <- factor(Larabee_Dolezaldata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Larabee_Dolezaldata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Larabee Creek - Dolezal") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Larabee Creek - Forney
```{r, echo=FALSE, warning=FALSE}
#get data
Larabee_Forneydata<- Larabee_Forney%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Larabee_Forneydata$tempRange = "Cool"
  Larabee_Forneydata$tempRange[Larabee_Forneydata$Temp < 68] <- "Cold"
  Larabee_Forneydata$tempRange[Larabee_Forneydata$Temp >= 77] <- "Warm"
  Larabee_Forneydata$tempRange <- factor(Larabee_Forneydata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Larabee_Forneydata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Larabee Creek - Forney") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Larabee Creek - School
```{r, echo=FALSE, warning=FALSE}
#get data
Larabee_Schooldata<- Larabee_School%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Larabee_Schooldata$tempRange = "Cool"
  Larabee_Schooldata$tempRange[Larabee_Schooldata$Temp < 68] <- "Cold"
  Larabee_Schooldata$tempRange[Larabee_Schooldata$Temp >= 77] <- "Warm"
  Larabee_Schooldata$tempRange <- factor(Larabee_Schooldata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Larabee_Schooldata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Larabee Creek - School") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Long Pine Creek - Site 2
```{r, echo=FALSE, warning=FALSE}
#get data
LongPine_Site2data<- LongPine_Site2%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  LongPine_Site2data$tempRange = "Cool"
  LongPine_Site2data$tempRange[LongPine_Site2data$Temp < 68] <- "Cold"
  LongPine_Site2data$tempRange[LongPine_Site2data$Temp >= 77] <- "Warm"
  LongPine_Site2data$tempRange <- factor(LongPine_Site2data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = LongPine_Site2data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Long Pine Creek - Site 2") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Long Pine Creek - Site 3
```{r, echo=FALSE, warning=FALSE}
#get data
LongPine_Site3data<- LongPine_Site3%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  LongPine_Site3data$tempRange = "Cool"
  LongPine_Site3data$tempRange[LongPine_Site3data$Temp < 68] <- "Cold"
  LongPine_Site3data$tempRange[LongPine_Site3data$Temp >= 77] <- "Warm"
  LongPine_Site3data$tempRange <- factor(LongPine_Site3data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = LongPine_Site3data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Long Pine Creek - Site 3") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Long Pine Creek - Site 4
```{r, echo=FALSE, warning=FALSE}
#get data
LongPine_Site4data<- LongPine_Site4%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Deadmansdata$tempRange = "Cool"
  Deadmansdata$tempRange[Deadmansdata$Temp < 68] <- "Cold"
  Deadmansdata$tempRange[Deadmansdata$Temp >= 77] <- "Warm"
  Deadmansdata$tempRange <- factor(Deadmansdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Deadmansdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Long Pine Creek - Site 4") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Long Pine Creek - Site 6
```{r, echo=FALSE, warning=FALSE}
#get data
LongPine_Site6data<- LongPine_Site6%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  LongPine_Site6data$tempRange = "Cool"
  LongPine_Site6data$tempRange[LongPine_Site6data$Temp < 68] <- "Cold"
  LongPine_Site6data$tempRange[LongPine_Site6data$Temp >= 77] <- "Warm"
  LongPine_Site6data$tempRange <- factor(LongPine_Site6data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = LongPine_Site6data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Long Pine Creek - Site 6") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Middle Loup River - Middle Branch
```{r, echo=FALSE, warning=FALSE}
#get data
MiddleLoup_MiddleBranchdata<- MiddleLoup_MiddleBranch%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  MiddleLoup_MiddleBranchdata$tempRange = "Cool"
  MiddleLoup_MiddleBranchdata$tempRange[MiddleLoup_MiddleBranchdata$Temp < 68] <- "Cold"
  MiddleLoup_MiddleBranchdata$tempRange[MiddleLoup_MiddleBranchdata$Temp >= 77] <- "Warm"
  MiddleLoup_MiddleBranchdata$tempRange <- factor(MiddleLoup_MiddleBranchdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = MiddleLoup_MiddleBranchdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Middle Loup River - Middle Branch") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Middle Loup River - Mullens
```{r, echo=FALSE, warning=FALSE}
#get data
MiddleLoup_Mullensdata<- MiddleLoup_Mullens%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  MiddleLoup_Mullensdata$tempRange = "Cool"
  MiddleLoup_Mullensdata$tempRange[MiddleLoup_Mullensdata$Temp < 68] <- "Cold"
  MiddleLoup_Mullensdata$tempRange[MiddleLoup_Mullensdata$Temp >= 77] <- "Warm"
  MiddleLoup_Mullensdata$tempRange <- factor(MiddleLoup_Mullensdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = MiddleLoup_Mullensdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Middle Loup River - Mullens") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Middle Loup River - South Branch
```{r, echo=FALSE, warning=FALSE}
#get data
MiddleLoup_SouthBranchdata<- MiddleLoup_SouthBranch%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  MiddleLoup_SouthBranchdata$tempRange = "Cool"
  MiddleLoup_SouthBranchdata$tempRange[MiddleLoup_SouthBranchdata$Temp < 68] <- "Cold"
  MiddleLoup_SouthBranchdata$tempRange[MiddleLoup_SouthBranchdata$Temp >= 77] <- "Warm"
  MiddleLoup_SouthBranchdata$tempRange <- factor(MiddleLoup_SouthBranchdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = MiddleLoup_SouthBranchdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Middle Loup River - South Branch") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Minnechaduza Creek - Site 1
```{r, echo=FALSE, warning=FALSE}
#get data
Minnechaduza_Site1data<- Minnechaduza_Site1%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Minnechaduza_Site1data$tempRange = "Cool"
  Minnechaduza_Site1data$tempRange[Minnechaduza_Site1data$Temp < 68] <- "Cold"
  Minnechaduza_Site1data$tempRange[Minnechaduza_Site1data$Temp >= 77] <- "Warm"
  Minnechaduza_Site1data$tempRange <- factor(Minnechaduza_Site1data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Minnechaduza_Site1data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Minnechaduza Creek - Site 1") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Minnechaduza Creek - Site 2
```{r, echo=FALSE, warning=FALSE}
#get data
Minnechaduza_Site2data<- Minnechaduza_Site2%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Minnechaduza_Site2data$tempRange = "Cool"
  Minnechaduza_Site2data$tempRange[Minnechaduza_Site2data$Temp < 68] <- "Cold"
  Minnechaduza_Site2data$tempRange[Minnechaduza_Site2data$Temp >= 77] <- "Warm"
  Minnechaduza_Site2data$tempRange <- factor(Minnechaduza_Site2data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Minnechaduza_Site2data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Minnechaduza Creek - Site 2") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Minnechaduza Creek - Site 3
```{r, echo=FALSE, warning=FALSE}
#get data
Minnechaduza_Site3data<- Minnechaduza_Site3%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Minnechaduza_Site3data$tempRange = "Cool"
  Minnechaduza_Site3data$tempRange[Minnechaduza_Site3data$Temp < 68] <- "Cold"
  Minnechaduza_Site3data$tempRange[Minnechaduza_Site3data$Temp >= 77] <- "Warm"
  Minnechaduza_Site3data$tempRange <- factor(Minnechaduza_Site3data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Minnechaduza_Site3data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Minnechaduza Creek - Site 3") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Monroe Creek
```{r, echo=FALSE, warning=FALSE}
#get data
Monroedata<- Monroe%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Monroedata$tempRange = "Cool"
  Monroedata$tempRange[Monroedata$Temp < 68] <- "Cold"
  Monroedata$tempRange[Monroedata$Temp >= 77] <- "Warm"
  Monroedata$tempRange <- factor(Monroedata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Monroedata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Monroe Creek") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Nine Mile Creek - Lower
```{r, echo=FALSE, warning=FALSE}
#get data
NineMileLowerdata<- NineMileLower%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  NineMileLowerdata$tempRange = "Cool"
  NineMileLowerdata$tempRange[NineMileLowerdata$Temp < 68] <- "Cold"
  NineMileLowerdata$tempRange[NineMileLowerdata$Temp >= 77] <- "Warm"
  NineMileLowerdata$tempRange <- factor(NineMileLowerdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = NineMileLowerdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Nine Mile Creek - Lower") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Nine Mile Creek - OFW
```{r, echo=FALSE, warning=FALSE}
#get data
NineMileOFWdata<- NineMileOFW%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  NineMileOFWdata$tempRange = "Cool"
  NineMileOFWdata$tempRange[NineMileOFWdata$Temp < 68] <- "Cold"
  NineMileOFWdata$tempRange[NineMileOFWdata$Temp >= 77] <- "Warm"
  NineMileOFWdata$tempRange <- factor(NineMileOFWdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = NineMileOFWdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Nine Mile Creek - OFW") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Nine Mile Creek - WMA
```{r, echo=FALSE, warning=FALSE}
#get data
NineMileWMAdata<- NineMileWMA%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  NineMileWMAdata$tempRange = "Cool"
  NineMileWMAdata$tempRange[NineMileWMAdata$Temp < 68] <- "Cold"
  NineMileWMAdata$tempRange[NineMileWMAdata$Temp >= 77] <- "Warm"
  NineMileWMAdata$tempRange <- factor(NineMileWMAdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = NineMileWMAdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Nine Mile Creek - WMA") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Niobrara River - Highway 71
```{r, echo=FALSE, warning=FALSE}
#get data
Niobrara_HWY71data<- Niobrara_HWY71%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Niobrara_HWY71data$tempRange = "Cool"
  Niobrara_HWY71data$tempRange[Niobrara_HWY71data$Temp < 68] <- "Cold"
  Niobrara_HWY71data$tempRange[Niobrara_HWY71data$Temp >= 77] <- "Warm"
  Niobrara_HWY71data$tempRange <- factor(Niobrara_HWY71data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Niobrara_HWY71data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Niobara River - Hwy 71") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Niobrara River - Highway 385
```{r, echo=FALSE, warning=FALSE}
#get data
Niobrara_HWY385data<- Niobrara_HWY385%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Niobrara_HWY385data$tempRange = "Cool"
  Niobrara_HWY385data$tempRange[Niobrara_HWY385data$Temp < 68] <- "Cold"
  Niobrara_HWY385data$tempRange[Niobrara_HWY385data$Temp >= 77] <- "Warm"
  Niobrara_HWY385data$tempRange <- factor(Niobrara_HWY385data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Niobrara_HWY385data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Niobrara River - Hwy 385") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Niobrara River - Pink Schoolhouse
```{r, echo=FALSE, warning=FALSE}
#get data
Niobrara_Schoolhousedata<- Niobrara_Schoolhouse%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Niobrara_Schoolhousedata$tempRange = "Cool"
  Niobrara_Schoolhousedata$tempRange[Niobrara_Schoolhousedata$Temp < 68] <- "Cold"
  Niobrara_Schoolhousedata$tempRange[Niobrara_Schoolhousedata$Temp >= 77] <- "Warm"
  Niobrara_Schoolhousedata$tempRange <- factor(Niobrara_Schoolhousedata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Niobrara_Schoolhousedata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Niobrara River - Pink Schoolhouse") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Pine Creek - Middle
```{r, echo=FALSE, warning=FALSE}
#get data
Pine_Middledata<- Pine_Middle%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Pine_Middledata$tempRange = "Cool"
  Pine_Middledata$tempRange[Pine_Middledata$Temp < 68] <- "Cold"
  Pine_Middledata$tempRange[Pine_Middledata$Temp >= 77] <- "Warm"
  Pine_Middledata$tempRange <- factor(Pine_Middledata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Pine_Middledata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Pine Creek - Middle") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Pine Creek - North
```{r, echo=FALSE, warning=FALSE}
#get data
Pine_Northdata<- Pine_North%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Pine_Northdata$tempRange = "Cool"
  Pine_Northdata$tempRange[Pine_Northdata$Temp < 68] <- "Cold"
  Pine_Northdata$tempRange[Pine_Northdata$Temp >= 77] <- "Warm"
  Pine_Northdata$tempRange <- factor(Pine_Northdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Pine_Northdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Pine Creek - North") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Pine Creek - South
```{r, echo=FALSE, warning=FALSE}
#get data
Pine_Southdata<- Pine_South%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Pine_Southdata$tempRange = "Cool"
  Pine_Southdata$tempRange[Pine_Southdata$Temp < 68] <- "Cold"
  Pine_Southdata$tempRange[Pine_Southdata$Temp >= 77] <- "Warm"
  Pine_Southdata$tempRange <- factor(Pine_Southdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Pine_Southdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Pine Creek - South") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Plum Creek - Site 1
```{r, echo=FALSE, warning=FALSE}
#get data
Plum_Site1data<- Plum_Site1%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Plum_Site1data$tempRange = "Cool"
  Plum_Site1data$tempRange[Plum_Site1data$Temp < 68] <- "Cold"
  Plum_Site1data$tempRange[Plum_Site1data$Temp >= 77] <- "Warm"
  Plum_Site1data$tempRange <- factor(Plum_Site1data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Plum_Site1data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Plum Creek - Site 1") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Plum Creek - Site 2
```{r, echo=FALSE, warning=FALSE}
#get data
Plum_Site2data<- Plum_Site2%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Plum_Site2data$tempRange = "Cool"
  Plum_Site2data$tempRange[Plum_Site2data$Temp < 68] <- "Cold"
  Plum_Site2data$tempRange[Plum_Site2data$Temp >= 77] <- "Warm"
  Plum_Site2data$tempRange <- factor(Plum_Site2data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Plum_Site2data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Plum Creek - Site 2") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Plum Creek - Site 3
```{r, echo=FALSE, warning=FALSE}
#get data
Plum_Site3data<- Plum_Site3%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Plum_Site3data$tempRange = "Cool"
  Plum_Site3data$tempRange[Plum_Site3data$Temp < 68] <- "Cold"
  Plum_Site3data$tempRange[Plum_Site3data$Temp >= 77] <- "Warm"
  Plum_Site3data$tempRange <- factor(Plum_Site3data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Plum_Site3data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Plum Creek - Site 3") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Plum Creek - Site 4
```{r, echo=FALSE, warning=FALSE}
#get data
Plum_Site4data<- Plum_Site4%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Plum_Site4data$tempRange = "Cool"
  Plum_Site4data$tempRange[Plum_Site4data$Temp < 68] <- "Cold"
  Plum_Site4data$tempRange[Plum_Site4data$Temp >= 77] <- "Warm"
  Plum_Site4data$tempRange <- factor(Plum_Site4data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Plum_Site4data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Plum Creek- Site 4") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Plum Creek - Site 5
```{r, echo=FALSE, warning=FALSE}
#get data
Plum_Site5data<- Plum_Site5%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Plum_Site5data$tempRange = "Cool"
  Plum_Site5data$tempRange[Plum_Site5data$Temp < 68] <- "Cold"
  Plum_Site5data$tempRange[Plum_Site5data$Temp >= 77] <- "Warm"
  Plum_Site5data$tempRange <- factor(Plum_Site5data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Plum_Site5data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Plum Creek - Site 5") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Plum Creek - Site 6
```{r, echo=FALSE, warning=FALSE}
#get data
Plum_Site6data<- Plum_Site6%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Plum_Site6data$tempRange = "Cool"
  Plum_Site6data$tempRange[Plum_Site6data$Temp < 68] <- "Cold"
  Plum_Site6data$tempRange[Plum_Site6data$Temp >= 77] <- "Warm"
  Plum_Site6data$tempRange <- factor(Plum_Site6data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Plum_Site6data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Plum Creek - Site 6") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Plum Creek - Site 7
```{r, echo=FALSE, warning=FALSE}
#get data
Plum_Site7data<- Plum_Site7%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Plum_Site7data$tempRange = "Cool"
  Plum_Site7data$tempRange[Plum_Site7data$Temp < 68] <- "Cold"
  Plum_Site7data$tempRange[Plum_Site7data$Temp >= 77] <- "Warm"
  Plum_Site7data$tempRange <- factor(Plum_Site7data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Plum_Site7data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Plum Creek - Site 7") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Plum Creek - Site 8
```{r, echo=FALSE, warning=FALSE}
#get data
Plum_Site8data<- Plum_Site8%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Plum_Site8data$tempRange = "Cool"
  Plum_Site8data$tempRange[Plum_Site8data$Temp < 68] <- "Cold"
  Plum_Site8data$tempRange[Plum_Site8data$Temp >= 77] <- "Warm"
  Plum_Site8data$tempRange <- factor(Plum_Site8data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Plum_Site8data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Plum Creek - Site 8") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Plum Creek - Site 9
```{r, echo=FALSE, warning=FALSE}
#get data
Plum_Site9data<- Plum_Site9%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Plum_Site9data$tempRange = "Cool"
  Plum_Site9data$tempRange[Plum_Site9data$Temp < 68] <- "Cold"
  Plum_Site9data$tempRange[Plum_Site9data$Temp >= 77] <- "Warm"
  Plum_Site9data$tempRange <- factor(Plum_Site9data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Plum_Site9data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Plum Creek - Site 9") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Dand Draw - Site 1
```{r, echo=FALSE, warning=FALSE}
#get data
SandDraw_Site1data<- SandDraw_Site1%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  SandDraw_Site1data$tempRange = "Cool"
  SandDraw_Site1data$tempRange[SandDraw_Site1data$Temp < 68] <- "Cold"
  SandDraw_Site1data$tempRange[SandDraw_Site1data$Temp >= 77] <- "Warm"
  SandDraw_Site1data$tempRange <- factor(SandDraw_Site1data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = SandDraw_Site1data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Sand Draw - Site 1") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Sand Draw - Site 2
```{r, echo=FALSE, warning=FALSE}
#get data
SandDraw_Site2data<- SandDraw_Site2%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  SandDraw_Site2data$tempRange = "Cool"
  SandDraw_Site2data$tempRange[SandDraw_Site2data$Temp < 68] <- "Cold"
  SandDraw_Site2data$tempRange[SandDraw_Site2data$Temp >= 77] <- "Warm"
  SandDraw_Site2data$tempRange <- factor(SandDraw_Site2data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = SandDraw_Site2data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Sand Draw - Site 2") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Schlagel Creek - New WMA
```{r, echo=FALSE, warning=FALSE}
#get data
Schlagel_newWMAdata<- Schlagel_newWMA%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Schlagel_newWMAdata$tempRange = "Cool"
  Schlagel_newWMAdata$tempRange[Schlagel_newWMAdata$Temp < 68] <- "Cold"
  Schlagel_newWMAdata$tempRange[Schlagel_newWMAdata$Temp >= 77] <- "Warm"
  Schlagel_newWMAdata$tempRange <- factor(Schlagel_newWMAdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Schlagel_newWMAdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Schlagel Creek - New WMA") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Schlagel Creek - Swanson
```{r, echo=FALSE, warning=FALSE}
#get data
Schlagel_Swansondata<- Schlagel_Swanson%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Schlagel_Swansondata$tempRange = "Cool"
  Schlagel_Swansondata$tempRange[Schlagel_Swansondata$Temp < 68] <- "Cold"
  Schlagel_Swansondata$tempRange[Schlagel_Swansondata$Temp >= 77] <- "Warm"
  Schlagel_Swansondata$tempRange <- factor(Schlagel_Swansondata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Schlagel_Swansondata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Schlagel Creek - Swanson") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Schlagel Creek - Vanderplow
```{r, echo=FALSE, warning=FALSE}
#get data
Schlagel_Vanderplowdata<- Schlagel_Vanderplow%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Schlagel_Vanderplowdata$tempRange = "Cool"
  Schlagel_Vanderplowdata$tempRange[Schlagel_Vanderplowdata$Temp < 68] <- "Cold"
  Schlagel_Vanderplowdata$tempRange[Schlagel_Vanderplowdata$Temp >= 77] <- "Warm"
  Schlagel_Vanderplowdata$tempRange <- factor(Schlagel_Vanderplowdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Schlagel_Vanderplowdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Schlagel Creek - Vanderplow") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Schlagel Creek - WMA
```{r, echo=FALSE, warning=FALSE}
#get data
Schlagel_WMAdata<- Schlagel_WMA%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Schlagel_WMAdata$tempRange = "Cool"
  Schlagel_WMAdata$tempRange[Schlagel_WMAdata$Temp < 68] <- "Cold"
  Schlagel_WMAdata$tempRange[Schlagel_WMAdata$Temp >= 77] <- "Warm"
  Schlagel_WMAdata$tempRange <- factor(Schlagel_WMAdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Schlagel_WMAdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Schlagel Creek - WMA") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Sheep Creek - Site 1
```{r, echo=FALSE, warning=FALSE}
#get data
Sheep_Site1data<- Sheep_Site1%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Sheep_Site1data$tempRange = "Cool"
  Sheep_Site1data$tempRange[Sheep_Site1data$Temp < 68] <- "Cold"
  Sheep_Site1data$tempRange[Sheep_Site1data$Temp >= 77] <- "Warm"
  Sheep_Site1data$tempRange <- factor(Sheep_Site1data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Sheep_Site1data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Sheep Creek - Site 1") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Sheep Creek - Site 2
```{r, echo=FALSE, warning=FALSE}
#get data
Sheep_Site2data<- Sheep_Site2%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Sheep_Site2data$tempRange = "Cool"
  Sheep_Site2data$tempRange[Sheep_Site2data$Temp < 68] <- "Cold"
  Sheep_Site2data$tempRange[Sheep_Site2data$Temp >= 77] <- "Warm"
  Sheep_Site2data$tempRange <- factor(Sheep_Site2data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Sheep_Site2data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Sheep Creek - Site 2") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Snake River - Adamson
```{r, echo=FALSE, warning=FALSE}
#get data
Snake_Adamsondata<- Snake_Adamson%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Snake_Adamsondata$tempRange = "Cool"
  Snake_Adamsondata$tempRange[Snake_Adamsondata$Temp < 68] <- "Cold"
  Snake_Adamsondata$tempRange[Snake_Adamsondata$Temp >= 77] <- "Warm"
  Snake_Adamsondata$tempRange <- factor(Snake_Adamsondata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Snake_Adamsondata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Snake River - Adamson") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Snake River - Highway 61
```{r, echo=FALSE, warning=FALSE}
#get data
Snake_HWY61data<- Snake_HWY61%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Snake_HWY61data$tempRange = "Cool"
  Snake_HWY61data$tempRange[Snake_HWY61data$Temp < 68] <- "Cold"
  Snake_HWY61data$tempRange[Snake_HWY61data$Temp >= 77] <- "Warm"
  Snake_HWY61data$tempRange <- factor(Snake_HWY61data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Snake_HWY61data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Snake River - Hwy 61") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Snake River - Upper
```{r, echo=FALSE, warning=FALSE}
#get data
Snake_Upperdata<- Monroe%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Snake_Upperdata$tempRange = "Cool"
  Snake_Upperdata$tempRange[Snake_Upperdata$Temp < 68] <- "Cold"
  Snake_Upperdata$tempRange[Snake_Upperdata$Temp >= 77] <- "Warm"
  Snake_Upperdata$tempRange <- factor(Snake_Upperdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Snake_Upperdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Snake River - Upper") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Soldier Creek - Middle Branch
```{r, echo=FALSE, warning=FALSE}
#get data
Soldier_MiddleBranchdata<- Soldier_MiddleBranch%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Soldier_MiddleBranchdata$tempRange = "Cool"
  Soldier_MiddleBranchdata$tempRange[Soldier_MiddleBranchdata$Temp < 68] <- "Cold"
  Soldier_MiddleBranchdata$tempRange[Soldier_MiddleBranchdata$Temp >= 77] <- "Warm"
  Soldier_MiddleBranchdata$tempRange <- factor(Soldier_MiddleBranchdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Soldier_MiddleBranchdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Soldier Creek - Middle Branch") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Sowbelly Creek
```{r, echo=FALSE, warning=FALSE}
#get data
Sowbellydata<- Sowbelly%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Sowbellydata$tempRange = "Cool"
  Sowbellydata$tempRange[Sowbellydata$Temp < 68] <- "Cold"
  Sowbellydata$tempRange[Sowbellydata$Temp >= 77] <- "Warm"
  Sowbellydata$tempRange <- factor(Sowbellydata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Sowbellydata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Sowbelly Creek") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# West Ash Creek - USFS
```{r, echo=FALSE, warning=FALSE}
#get data
WestAsh_USFSdata<- WestAsh_USFS%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  WestAsh_USFSdata$tempRange = "Cool"
  WestAsh_USFSdata$tempRange[WestAsh_USFSdata$Temp < 68] <- "Cold"
  WestAsh_USFSdata$tempRange[WestAsh_USFSdata$Temp >= 77] <- "Warm"
  WestAsh_USFSdata$tempRange <- factor(WestAsh_USFSdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = WestAsh_USFSdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="West Ash Creek - USFS") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# White River - Andrews
```{r, echo=FALSE, warning=FALSE}
#get data
White_Andrewsdata<- White_Andrews%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  White_Andrewsdata$tempRange = "Cool"
  White_Andrewsdata$tempRange[White_Andrewsdata$Temp < 68] <- "Cold"
  White_Andrewsdata$tempRange[White_Andrewsdata$Temp >= 77] <- "Warm"
  White_Andrewsdata$tempRange <- factor(White_Andrewsdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = White_Andrewsdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="White River - Andrews") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# White River - East Fort Rob
```{r, echo=FALSE, warning=FALSE}
#get data
White_EastFtRobdata<- White_EastFtRob%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  White_EastFtRobdata$tempRange = "Cool"
  White_EastFtRobdata$tempRange[White_EastFtRobdata$Temp < 68] <- "Cold"
  White_EastFtRobdata$tempRange[White_EastFtRobdata$Temp >= 77] <- "Warm"
  White_EastFtRobdata$tempRange <- factor(White_EastFtRobdata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = White_EastFtRobdata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="White River - East Fort Rob") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# White River = Golf Course 
```{r, echo=FALSE, warning=FALSE}
#get data
White_GolfCoursedata<- White_GolfCourse%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  White_GolfCoursedata$tempRange = "Cool"
  White_GolfCoursedata$tempRange[White_GolfCoursedata$Temp < 68] <- "Cold"
  White_GolfCoursedata$tempRange[White_GolfCoursedata$Temp >= 77] <- "Warm"
  White_GolfCoursedata$tempRange <- factor(White_GolfCoursedata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = White_GolfCoursedata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="White River - Golf Course") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# White River - Swinging Bridge
```{r, echo=FALSE, warning=FALSE}
#get data
White_SwingingBridgedata<- White_SwingingBridge%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  White_SwingingBridgedata$tempRange = "Cool"
  White_SwingingBridgedata$tempRange[White_SwingingBridgedata$Temp < 68] <- "Cold"
  White_SwingingBridgedata$tempRange[White_SwingingBridgedata$Temp >= 77] <- "Warm"
  White_SwingingBridgedata$tempRange <- factor(White_SwingingBridgedata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = White_SwingingBridgedata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="White River - Swinging Bridge") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# White Clay Creek
```{r, echo=FALSE, warning=FALSE}
#get data
WhiteClaydata<- WhiteClay%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  WhiteClaydata$tempRange = "Cool"
  WhiteClaydata$tempRange[WhiteClaydata$Temp < 68] <- "Cold"
  WhiteClaydata$tempRange[WhiteClaydata$Temp >= 77] <- "Warm"
  WhiteClaydata$tempRange <- factor(WhiteClaydata$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = WhiteClaydata) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="White Clay Creek") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```

# Willow Creek - Site 1
```{r, echo=FALSE, warning=FALSE}
#get data
Willow_Site1data<- Willow_Site1%>% # change name to whatever waterbody_site you'd like to examine
    mutate(DateTime = as.Date(DateTime, origin = "1960-10-01")) %>%
    mutate(year = format(DateTime, "%Y")) %>%
    mutate(jul = format(DateTime,  "%j"))# new_date = julian2date(julian_date)) 

#create temp range
  #this function assigns color values to the temps
  ## I have classified streams into three different categories based on the Cool Water Streams Management Plan by NGPC (2016-2020).
  ### cold =<68F, cool= 68.1-76.9, warm >=77
  Willow_Site1data$tempRange = "Cool"
  Willow_Site1data$tempRange[Willow_Site1data$Temp < 68] <- "Cold"
  Willow_Site1data$tempRange[Willow_Site1data$Temp >= 77] <- "Warm"
  Willow_Site1data$tempRange <- factor(Willow_Site1data$tempRange, levels=c("Cold", "Cool", "Warm"))
  
  #create plot
ggplot(data = Willow_Site1data) +
    geom_point(aes(x = DateTime, y = Temp, color = tempRange), size = .5) +
    geom_smooth(aes(x = DateTime, y = Temp), color = "green", size = 1) +
    labs(x = "", y = "Water Temperature (degrees F)", title = "Hourly Water Temps", subtitle ="Willow Creek - Site 1") + # !!! don't forget to change graph title!!!
    scale_y_continuous(limits = c(10,100)) +
    scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 month", date_labels = "%b-%Y") +
    scale_color_manual(values = c("navy", "cadetblue", "darkred")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.major = element_line(color = "gray70"),
          panel.background = element_rect(fill = "gray90"),
          title = element_text(hjust = 0.5,
                               color = "black"),
          strip.background = element_rect(fill = "white"),
          strip.text = element_text(color = "gray20"),
          axis.text = element_text(color = "black"),
          legend.title = element_blank())
```