#An Introduction to Temperature

Temperature has been described as the abiotic master factor when it comes to fishes (See Fry 1971, Brett 1971) but it is also immensly important when talking about anything aquatic. Temperature, along with flow, are primary driving factors in stream ecosystems and therefore should be of preeminant import and its relative ease of capture in the field. 

## Cleaning up the Data

First, we need to import the data. We have an xcell file ~`templogger2020` that is a collection of all data from 2015-2020 (ish), consisting of *min*, *mean*, and *max*. Each sheet must be brought in seperately, and there are plenty of errors per sheet. This data can't really be used as is and needs a lot of cleaning. However, we will use that data to double check our raw data which we are compiling into a single `masterData` file. 

## Raw Data

### Alliance Drain 1

```{r}
##6/16/2020

library(tidyverse)

AllianceDrain2015 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/Done/AllianceDrainSite1_2015.csv", col_names = TRUE, na = "NA")

AllianceDrain2016 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/Done/AllianceDrainSite1_2016.csv", col_names = TRUE, na = "NA")

rbind(AllianceDrain2015, AllianceDrain2016) -> AllianceMasterData

AllianceMasterData %>% 
  separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Stream = "Alliance Drain",
         Site = "Site 1",
         Date = lubridate::mdy(Date),
         Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9)),
         Basin = "Niobrara",
         Water = "Coolwater",
         Lat = "42.56561",
         Long = "-100.121",
         Deployment = "Seasonal") %>% 
  select(-ID) %>% 
  select(-Location) -> AllianceMasterData

```


### Bone Creek

```{r}
##6/16/2020
### Site 1

BoneCreekSite1_2015 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/Done/BoneCreekSite1_2015.csv", col_names = TRUE, na = "NA")

BoneCreekSite1_2015 %>% 
  separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Stream = "Bone Creek",
         Site = "Site 1 Grewcock",
         Date = lubridate::mdy(Date),
         Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9)),
         Basin = "Niobrara",
         Water = "Warmwater",
         Lat = "42.68207",
         Long = "-99.69564",
         Deployment = "Seasonal") %>% 
  select(-ID) %>% 
  select(-Location) -> BoneCreek1

BoneCreekSite2_2015 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/Done/BoneCreekSite2_2015.csv", col_names = TRUE, na = "NA")

BoneCreekSite2_2015 %>% 
  separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Stream = "Bone Creek",
         Site = "Site 2 Keller Park SRA",
         Date = lubridate::mdy(Date),
         Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9)),
         Basin = "Niobrara",
         Water = "Warmwater",
         Lat = "42.67097",
         Long = "-99.76698",
         Deployment = "Seasonal") %>% 
  select(-ID) %>% 
  select(-Location) -> BoneCreek2

BoneCreekSite3_2015 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/Done/BoneCreekSite3_2015.csv", col_names = TRUE, na = "NA")

BoneCreekSite3_2015 %>% 
  separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Stream = "Bone Creek",
         Site = "Site 3 Keller WMA",
         Date = lubridate::mdy(Date),
         Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9)),
         Basin = "Niobrara",
         Water = "Warmwater",
         Lat = "42.6656",
         Long = "-99.77757",
         Deployment = "Seasonal") %>% 
  select(-ID) %>% 
  select(-Location) -> BoneCreek3


#Read in bone creek #4
BoneCreekSite4_2015 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/Done/BoneCreekSite4_2015.csv", col_names = TRUE, na = "NA")

BoneCreekSite4_2016 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/Done/BoneCreekSite4_2016.csv", col_names = TRUE, na = "NA")

rbind(BoneCreekSite4_2015, BoneCreekSite4_2016) -> BoneCreek4

BoneCreek4 %>% 
  separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Stream = "Bone Creek",
         Site = "Site 4 Sisson",
         Date = lubridate::mdy(Date),
         Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9)),
         Basin = "Niobrara",
         Water = "Warmwater",
         Lat = "42.59239",
         Long = "-99.81621") %>% 
  select(-ID) %>% 
  select(-Location) -> BoneCreek4

BoneCreek4 %>% 
  mutate(Deployment = "Seasonal") -> BoneCreek4

rbind(BoneCreek1, BoneCreek2, BoneCreek3, BoneCreek4) -> BoneCreekMasterData

```


###Bordeaux Cliffs

```{r}
##6/16/2020
###Bordeaux Cliffs 

BordCreekCliffs_2016 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/Done/BordeauxCreekCliffs_2016.csv", col_names = TRUE, na = "NA")

BordCreekCliffs_2017 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/BordeauxCreekCliffs_2017.csv", col_names = TRUE, na = "NA")

rbind(BordCreekCliffs_2016, BordCreekCliffs_2017) -> BordCliffsMasterData

BordCliffsMasterData %>% 
  separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Stream = "Bone Creek",
         Site = "Site 4 Sisson",
         Date = lubridate::mdy(Date),
         Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9)),
         Basin = "White-Hat",
         Water = "Warmwater",
         Lat = "42.71766",
         Long = "-102.9306",
         Deployment = "Year-round") %>% 
  select(-ID) %>% 
  select(-Location) -> BordCreekCliffsMasterData

```

### Bordeaux North

```{r}
library(tidyverse)

BordCreek2015 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/Done/BordeauxCreekNorth_2015.csv", col_names = TRUE, na = "NA")

BordCreek2016_1 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/Done/BordeauxCreekNorth_2016.csv", col_names = TRUE, na = "NA")

BordCreek2016_2 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/Done/BordeauxCreekNorth_2016_2.csv", col_names = TRUE, na = "NA")

BordCreek2017 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/BordeauxCreekNorth_2017.csv", col_names = TRUE, na = "NA")

rbind(BordCreek2015, BordCreek2016_1, BordCreek2016_2, BordCreek2017) -> BordeauxMasterData

BordeauxMasterData %>% 
separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Date = lubridate::mdy(Date)) -> BordeauxMasterData

BordeauxMasterData %>% 
mutate(Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9))) -> BordeauxMasterData

BordeauxMasterData %>% 
  mutate(Lat = "42.8097",
         Long = "-102.9221") -> BordeauxMasterData

BordeauxMasterData %>% 
  mutate(Basin = "White-Hat",
         Water = "Warmwater") -> BordeauxMasterData

BordeauxMasterData %>% 
  mutate(Stream = "Bordeaux Creek",
         Site = "North") -> BordeauxMasterData

select(BordeauxMasterData, -ID) -> BordeauxMasterData
select(BordeauxMasterData, -Location) -> BordeauxMasterData

# write_csv(BordeauxData, "C:/Users/alex.engel/Documents/GitHub/templogger/BordeauxData.csv")

BordeauxMasterData %>% 
  mutate(Deployment = "Year-round") -> BordeauxMasterData

head(BordeauxMasterData)
tail(BordeauxMasterData)
```

###Cedar River

```{r}
CedarRiver <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/CedarRiverSite1_2015.csv", col_names = TRUE, na = "NA")

CedarRiver %>% 
  rename(ID = D) -> CedarRiver

CedarRiver2 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/CedarRiverSite1_2016.csv", col_names = TRUE, na = "NA")

rbind(CedarRiver, CedarRiver2) -> CedarRiverMaster

CedarRiverMaster %>% 
  separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Stream = "Cedar Creek",
         Site = "Site 1",
         Date = lubridate::mdy(Date),
         Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9)),
         Basin = "Niobrara",
         Water = "Warmwater",
         Lat = "42.59689",
         Long = "-100.1529",
         Deployment = "Seasonal") %>% 
  select(-ID) %>% 
  select(-Location) -> CedarRiverMaster

```


###Chadron Creek Above Discharge
```{r}

ChadCreekAbove <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/Done/ChadronCreekAboveDischarge_2015.csv", col_names = TRUE, na = "NA")

ChadCreekAbove2016 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/Done/ChadronCreekAboveDischarge_2016.csv", col_names = TRUE, na = "NA")

rbind(ChadCreekAbove, ChadCreekAbove2016) -> ChadCreekAboveMaster

ChadCreekAboveMaster %>% 
  separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Stream = "Chadron Creek",
         Site = "Above Discharge",
         Date = lubridate::mdy(Date),
         Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9)),
         Basin = "White-Hat",
         Water = "Coolwater",
         Lat = "42.70919",
         Long = "-103.0097",
         Deployment = "Year-round") %>% 
  select(-ID) %>% 
  select(-Location) -> ChadCreekAboveMaster

```

###Nine Mile OFW

```{r}
library(tidyverse)

NineMileCreekOFW <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/Done/NineMileCreekOFW_2016.csv", col_names = TRUE, na = "NA")

NineMileCreekOFW %>% 
  separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Stream = "Nine Mile Creek",
         Site = "OFW",
         Date = lubridate::mdy(Date),
         Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9)),
         Basin = "North Platte",
         Water = "Coolwater",
         Lat = "41.87352",
         Long = "-103.4372",
         Deployment = "Year-round") %>% 
  select(-ID) %>% 
  select(-Location) -> NineMileCreekOFWmaster


```

###Nine Mile WMA

```{r}

NineMileCreekWMA_2015 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/NineMileCreekWMA_2015.csv", col_names = TRUE, na = "NA")

NineMileCreekWMA_2016 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/NineMileCreekWMA_2016.csv", col_names = TRUE, na = "NA")

NineMileCreekWMA_2017 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/Done/NineMileCreekWMA_2017.csv", col_names = TRUE, na = "NA")

NineMileCreekWMA_2017_2 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/Done/NineMileCreekWMA_2017_2.csv", col_names = TRUE, na = "NA")

rbind(NineMileCreekWMA_2015, NineMileCreekWMA_2016, NineMileCreekWMA_2017, NineMileCreekWMA_2017_2) -> NineMileCreekWMAmaster

NineMileCreekWMAmaster %>% 
  separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Stream = "Nine Mile Creek",
         Site = "WMA",
         Date = lubridate::mdy(Date),
         Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9)),
         Basin = "North Platte",
         Water = "Coolwater",
         Lat = "41.89251",
         Long = "-103.433",
         Deployment = "Year-round") %>% 
  select(-ID) %>% 
  select(-Location) -> NineMileCreekWMAmaster
```

###White River Andrews

```{r}
WhiteRiverAndrews <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/WhiteRiverAndrews_2015.csv", col_names = TRUE, na = "NA")

WhiteRiverAndrews_2016 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/WhiteRiverAndrews_2016.csv", col_names = TRUE, na = "NA")

rbind(WhiteRiverAndrews, WhiteRiverAndrews_2016) -> WhiteRiverAndrewsMaster

WhiteRiverAndrewsMaster %>% 
  separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Stream = "White River",
         Site = "Andrews",
         Date = lubridate::mdy(Date),
         Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9)),
         Basin = "White-Hat",
         Water = "Coolwater",
         Lat = "42.63016",
         Long = "-103.7357",
         Deployment = "Year-round") %>% 
  select(-ID) %>% 
  select(-Location) -> WhiteRiverAndrewsMaster

```

###Deadmans Creek 
```{r}
library(tidyverse)

DeadmansCreek_2016 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/Done/DeadmansCreek_2016.csv", col_names = TRUE, na = "NA")

DeadmansCreek_2016 %>% 
  select(c(1:4)) %>% 
  separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Stream = "Deadmans Creek",
         Site = "Site 1",
         Date = lubridate::mdy(Date),
         Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9)),
         Basin = "White-Hat",
         Water = "Coolwater",
         Lat = "42.62613",
         Long = "-103.4999",
         Deployment = "Seasonal") %>% 
  select(-ID) %>% 
  select(-Location) -> DeadmansCreekMaster

DeadmansCreekMaster[c(4,5,1,7,6,8,2,3,9,10,11,12,13,14)] -> DeadmansCreekMaster
```

###Dismal River Dunning

```{r}
DismalRiverDunning_2017 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/DismalRiverDunning_2017.csv", col_names = TRUE, na = "NA")

DismalRiverDunning_2017 %>% 
  select(c(1:4)) %>% 
  separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Stream = "Dismal River",
         Site = "Dunning",
         Date = lubridate::mdy(Date),
         Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9)),
         Basin = "Loup",
         Water = "Warmwater",
         Lat = "41.82251",
         Long = "-100.1011",
         Deployment = "Seasonal") %>% 
  select(-ID) %>% 
  select(-Location) -> DismalRiverDunningMaster

DismalRiverDunningMaster[c(4,5,1,7,6,8,2,3,9,10,11,12,13,14)] -> DismalRiverDunningMaster
```

###Dry Creek
```{r}
DryCreekNumber1_2015 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/DryCreekNumber1_2015.csv", col_names = TRUE, na = "NA")

select(DryCreekNumber1_2015, c(1:4)) -> DryCreekNumber1_2015

DryCreekNumber1_2016 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/DryCreekNumber1_2016.csv", col_names = TRUE, na = "NA")

select(DryCreekNumber1_2016, c(1:4)) -> DryCreekNumber1_2016

DryCreekNumber1_2017 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/DryCreekNumber1_2017.csv", col_names = TRUE, na = "NA")

select(DryCreekNumber1_2017, c(1:4)) -> DryCreekNumber1_2017

DryCreekNumber1_2017_2 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/DryCreekNumber1_2017_2.csv", col_names = TRUE, na = "NA")

select(DryCreekNumber1_2017_2, c(1:4)) -> DryCreekNumber1_2017_2

rbind(DryCreekNumber1_2015, DryCreekNumber1_2016, DryCreekNumber1_2017, DryCreekNumber1_2017_2) -> DryCreekMaster

DryCreekMaster %>% 
  select(c(1:4)) %>% 
  separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Stream = "Dry Creek",
         Site = "#1",
         Date = lubridate::mdy(Date),
         Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9)),
         Basin = "Niobrara",
         Water = "Warmwater",
         Lat = "42.57188",
         Long = "-100.1716",
         Deployment = "Year-round") %>% 
  select(-ID) %>% 
  select(-Location) -> DryCreekMaster

DryCreekMaster[c(4,5,1,7,6,8,2,3,9,10,11,12,13,14)] -> DryCreekMaster
```

###East Ash Creek
```{r}
EastAshCreekUSFS_2016 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/EastAshCreekUSFS_2016.csv", col_names = TRUE, na = "NA")

select(EastAshCreekUSFS_2016, c(1:4)) -> EastAshCreekUSFS_2016

EastAshCreekUSFS_2017 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/EastAshCreekUSFS_2017.csv", col_names = TRUE, na = "NA")

select(EastAshCreekUSFS_2017, c(1:4)) -> EastAshCreekUSFS_2017

EastAshCreekUSFS_2018 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/EastAshCreekUSFS_2018.csv", col_names = TRUE, na = "NA")

select(EastAshCreekUSFS_2018, c(1:4)) -> EastAshCreekUSFS_2018

rbind(EastAshCreekUSFS_2016, EastAshCreekUSFS_2017, EastAshCreekUSFS_2018) -> EastAshCreekMaster

EastAshCreekMaster %>% 
  select(c(1:4)) %>% 
  separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Stream = "East Ash Creek",
         Site = "USFS",
         Date = lubridate::mdy(Date),
         Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9)),
         Basin = "White-Hat",
         Water = "Warmwater",
         Lat = "42.62373",
         Long = "-103.1904",
         Deployment = "Year-round") %>% 
  select(-ID) %>% 
  select(-Location) -> EastAshCreekMaster

EastAshCreekMaster[c(4,5,1,7,6,8,2,3,9,10,11,12,13,14)] -> EastAshCreekMaster

str(EastAshCreekMaster)

as_datetime()

str(MasterData)
```

###Long Pine
```{r}
library(tidyverse)
#6/24/2020

#Long Pine Number 1
LongPineNumber1_2015 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/LongPineNumber1_2015.csv", col_names = TRUE, na = "NA")

select(LongPineNumber1_2015, c(1:4)) -> LongPineNumber1_2015

LongPineNumber1_2015 %>% 
  select(c(1:4)) %>% 
  separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Stream = "Long Pine Creek",
         Site = "#1",
         Date = lubridate::mdy(Date),
         Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9)),
         Basin = "Niobrara",
         Water = "Coolwater",
         Lat = "42.70924",
         Long = "- 99.64276",
         Deployment = "Year-round") %>% 
  select(-ID) %>% 
  select(-Location) -> LongPineNumber1

LongPineNumber1[c(4,5,1,7,6,8,2,3,9,10,11,12,13,14)] -> LongPineNumber1

#Long Pine Number 2
LongPineNumber2_2015 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/LongPineNumber2_2015.csv", col_names = TRUE, na = "NA")

select(LongPineNumber2_2015, c(1:4)) -> LongPineNumber2_2015

LongPineNumber2_2016 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/LongPineNumber2_2016.csv", col_names = TRUE, na = "NA")

select(LongPineNumber2_2016, c(1:4)) -> LongPineNumber2_2016

LongPineNumber2_2017 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/LongPineNumber2_2017.csv", col_names = TRUE, na = "NA")

select(LongPineNumber2_2017, c(1:4)) -> LongPineNumber2_2017

rbind(LongPineNumber2_2015, LongPineNumber2_2016, LongPineNumber2_2017) -> LongPineNumber2

LongPineNumber2 %>% 
  select(c(1:4)) %>% 
  separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Stream = "Long Pine Creek",
         Site = "#2",
         Date = lubridate::mdy(Date),
         Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9)),
         Basin = "Niobrara",
         Water = "Coolwater",
         Lat = "42.67914",
         Long = "-99.69636",
         Deployment = "Year-round") %>% 
  select(-ID) %>% 
  select(-Location) -> LongPineNumber2

LongPineNumber2[c(4,5,1,7,6,8,2,3,9,10,11,12,13,14)] -> LongPineNumber2

##LongPineNumber3

LongPineNumber3_2015 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/LongPineNumber3_2015.csv", col_names = TRUE, na = "NA")

select(LongPineNumber3_2015, c(1:4)) -> LongPineNumber3_2015

LongPineNumber3_2016 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/LongPineNumber3_2016.csv", col_names = TRUE, na = "NA")

select(LongPineNumber3_2016, c(1:4)) -> LongPineNumber3_2016

LongPineNumber3_2016_2 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/LongPineNumber3_2016_2.csv", col_names = TRUE, na = "NA")

select(LongPineNumber3_2016_2, c(1:4)) -> LongPineNumber3_2016_2

LongPineNumber3_2017 <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/Data/ReadyforR/LongPineNumber3_2017.csv", col_names = TRUE, na = "NA")

select(LongPineNumber3_2017, c(1:4)) -> LongPineNumber3_2017

rbind(LongPineNumber3_2015, LongPineNumber3_2016, LongPineNumber3_2016_2, LongPineNumber3_2017) -> LongPineNumber3

LongPineNumber3 %>% 
  select(c(1:4)) %>% 
  separate(DateTime, c("Date", "Time"), sep = " ") %>% 
  mutate(Stream = "Long Pine Creek",
         Site = "#3",
         Date = lubridate::mdy(Date),
         Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (TempF - 32 *(5/9)),
         Basin = "Niobrara",
         Water = "Coolwater",
         Lat = "42.67914",
         Long = "-99.69636",
         Deployment = "Year-round") %>% 
  select(-ID) %>% 
  select(-Location) -> LongPineNumber3

LongPineNumber3[c(4,5,1,7,6,8,2,3,9,10,11,12,13,14)] -> LongPineNumber3

```


#Creating the Master File

rbind all `MasterData` files together.

```{r}
#216,476 obs. of 14 vars

# rbind(AllianceMasterData,
#       BordeauxMasterData, 
#       BordCreekCliffsMasterData, 
#       BoneCreekMasterData,
#       CedarRiverMaster) -> MasterData

#315,125 obs. of 14 vars
# rbind(ChadCreekAboveMaster,
      # NineMileCreekOFWmaster,
      # NineMileCreekWMAmaster,
      # WhiteRiverAndrewsMaster) -> MasterData1



MasterData %>% 
  mutate(Time = as.character(Time)) -> MasterData

str(MasterData)

#497704 obs. of 14 vars
# rbind(MasterData,
#       DeadmansCreekMaster,
#       DismalRiverDunningMaster,
#       DryCreekMaster,
#       EastAshCreekMaster) -> MasterData

head(MasterData)
tail(MasterData)

EastAshCreekMaster %>% 
  summarise(na = sum(is.na(Time)))

# MasterData1[c(4,5,1,7,6,8,2,3,9,10,11,12,13,14)] -> MasterData1

head(MasterData1)

# rbind(MasterData, MasterData1) -> MasterData



write_csv(MasterData, "C:/Users/alex.engel/Documents/GitHub/templogger/MasterData.csv")

str(MasterData)
```


```{r}
library(tidyverse)

MasterData <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/MasterData.csv", col_names = TRUE, na = "NA")

# MasterData[c(4,5,1,7,6,8,2,3,9,10,11,12,13,14)] -> MasterData

str(MasterData)


```



#Summary Data

```{r}
## 5/21/2020
library(tidyverse)
library(readr)

### Bordeaux ###
BordeauxCreekSum <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/2020TempLog/Bordeaux_Crk_Summary.csv", col_names = TRUE, na = "NA")

BordeauxWMA <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/2020TempLog/Bordeaux_WMA.csv", col_names = TRUE, na = "NA")

### Chadron Creek ###

ChradronCreekSum <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/2020TempLog/Chadron_Crkexit_Summary.csv", col_names = TRUE, na = "NA")

### Ash Creek ###

EastAshCreekSum <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/2020TempLog/EAsh_CrkUSFS_Summary.csv", col_names = TRUE, na = "NA")

```


```{r, temploggerXL}
library (tidyverse)
library(readxl)

stringsAsFactors = TRUE

Data2015 <- read_excel("C:/Users/alex.engel/Documents/GitHub/templogger/templogger2020.xlsx", sheet = 1)

Data2016 <- read_excel("C:/Users/alex.engel/Documents/GitHub/templogger/templogger2020.xlsx", sheet = 2)

Data2017 <- read_excel("C:/Users/alex.engel/Documents/GitHub/templogger/templogger2020.xlsx", sheet = 3)

Data2018 <- read_excel("C:/Users/alex.engel/Documents/GitHub/templogger/templogger2020.xlsx", sheet = 4)

Data2019 <- read_excel("C:/Users/alex.engel/Documents/GitHub/templogger/templogger2020.xlsx", sheet = 5)

Data2020 <- read_excel("C:/Users/alex.engel/Documents/GitHub/templogger/templogger2020.xlsx", sheet = 6)

Locations <- read_excel("C:/Users/alex.engel/Documents/GitHub/templogger/templogger2020.xlsx", sheet = 7)

```


#Raw Data Example

```{r, rawLogs}
library(tidyverse)

## 5/21/2020

BordeauxWMA <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/2020TempLog/rawBordeaux.csv", col_names = TRUE, na = "NA")

BordeauxWMA %>% 
  rename("Number" = "ID",
         "Datetime" = "Date Time",
         "Temp" = "Temp_Farenheight") -> BordeauxWMA

BordeauxWMA %>% 
  mutate(Location = "Bordeaux WMA") -> BordeauxWMA

head(BordeauxWMA)

ChadronCreek <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/2020TempLog/Chadron_Creek_Park_Exit.csv", col_names = TRUE, na = "NA")

ChadronCreek %>% 
  mutate(Location = "Chadron Creek (Park Exit)") -> ChadronCreek

head(ChadronCreek)


EastAshCreek <- read_csv("C:/Users/alex.engel/Documents/GitHub/templogger/2020TempLog/East_Ash_Creek_USFS.csv", col_names = TRUE, na = "NA")

head(EastAshCreek)

EastAshCreek %>% 
  mutate(Location = "East Ash Creek") -> EastAshCreek

head(EastAshCreek)

rbind(BordeauxWMA, ChadronCreek, EastAshCreek) -> rawData

## 5/21/2020

library(dplyr)
library(tidyr)
library(lubridate)

rawData %>% 
  separate(Datetime, c("Date", "Time"), sep = " ") %>% 
  mutate(Date = lubridate::mdy(Date)) -> rawData

rawData %>% 
  mutate(Month = lubridate::month(Date),
         Year = lubridate::year(Date),
         Day = lubridate::day(Date),
         TempC = (Temp - 32 *(5/9))) -> rawData

rawData %>% 
  rename(TempF = Temp) -> rawData

head(rawData)

write_csv(rawData, "C:/Users/alex.engel/Documents/GitHub/templogger/rawData.csv")
```